```{r echo=FALSE, warning=FALSE}
date=Sys.Date()
date=as.character(format(date,format="%Y%m%d"))
plate=df$plate[1]
condition=df$drug[1]
```

SCORE Report: `r date` - Plate `r plate` `r condition`
========================================================

Strain information:
```{r echo = FALSE, warning=FALSE}
options(width = 110)
strains=df$strain
```


Contaminated wells:
```{r echo=FALSE, warning=FALSE}
unlist(contamination[as.character(contamination$assay)==as.character(df$assay[1]) & as.numeric(contamination$plate)==as.numeric(df$plate[1]), "contam"])
```


Possibly contaminated wells:
```{r echo=FALSE, warning=FALSE}
possContam(df)
```


NA Count:
```{r echo=FALSE, warning=FALSE}
nrow(df[as.numeric(as.numeric(df$col)) %% 2 == 1 & is.na(df$n),])
```


NA Strains:
```{r echo=FALSE, warning=FALSE}
df[as.numeric(as.numeric(df$col)) %% 2 == 1 & is.na(df$n),"strain"]
```


Number of worms in each well:
```{r echo=FALSE,fig.width=15,fig.height=10, warning=FALSE}
ggplot(df) +
    geom_rect(aes(xmin=0,xmax=5,ymin=0,ymax=5,fill=ifelse(is.na(norm.n)|is.infinite(norm.n), NA, as.numeric(n)))) +
    facet_grid(row~col) +
    geom_text(aes(x=2.5,y=2.5,label=ifelse(is.na(norm.n), "NA", round(as.numeric(n), 2))),colour="white") +
    presentation+theme(axis.ticks.x=element_blank(), axis.ticks.y=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank()) +
    xlab("columns") +
    ylab("rows") +
    labs(title=paste0("Score p",df$plate[1]," Population"))
```



+ Top left: Mean TOF
+ Top right: Mean EXT
+ Bottom left: Median TOF
+ Bottom right: Median EXT
```{r echo=FALSE,fig.width=15,fig.height=10, warning=FALSE}
ggplot(df) +
    geom_rect(fill=NA,aes(xmin=0,xmax=5,ymin=0,ymax=5))+facet_grid(row~col) +
    geom_text(aes(x=1,y=4,label=ifelse(is.na(mean.TOF), "NA", round(mean.TOF, 0)))) +
    geom_text(aes(x=4,y=4,label=ifelse(is.na(mean.EXT), "NA", round(mean.EXT, 0)))) +
    geom_text(aes(x=1,y=1,label=ifelse(is.na(median.TOF), "NA", round(median.TOF, 0)))) +
    geom_text(aes(x=4,y=1,label=ifelse(is.na(median.EXT), "NA", round(mean.EXT, 0)))) +
    presentation +
    theme(axis.ticks.x=element_blank(), axis.ticks.y=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank()) +
    xlab("columns") +
    ylab("rows") +
    labs(title=paste0("Score p",df$plate[1]," TOF/EXT"))
```



Red fluorescence (normalized by mean TOF):
+ Top left: Mean red
+ Bottom right: Median red
```{r echo=FALSE,fig.width=15,fig.height=10, warning=FALSE}
ggplot(df) +
    geom_rect(aes(xmin=0,xmax=5,ymin=0,ymax=5),fill=NA) +
    facet_grid(row~col) +
    geom_text(aes(x=1,y=4,label=ifelse(is.na(mean.norm.red), "NA", round(mean.norm.red, 2)))) +
    geom_text(aes(x=4,y=1,label=ifelse(is.na(median.norm.red), "NA", round(median.norm.red, 2)))) +
    presentation +
    theme(axis.ticks.x=element_blank(), axis.ticks.y=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank()) +
    xlab("columns") +
    ylab("rows") +
    labs(title=paste0("Score p",df$plate[1]," Red Fluorescence"))
```



Life-stage distribution:
```{r echo=FALSE, warning=FALSE}
ggplot(melted.proc,aes(as.factor(col),value,fill=variable))+
    geom_bar(aes(x=3),stat="identity",position="stack") +
    facet_grid(row~col) +
    presentation +
    theme(axis.ticks.x=element_blank(), axis.ticks.y=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank()) +
    xlab("columns") +
    ylab("rows") +
    labs(title=paste0("Score p",df$plate[1]," Life-stage Distribution"))
```



Processed dataset:
```{r echo=FALSE, warning=FALSE}
df
```